---
title: "Lab 9"
author: "Skyler Moomey"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task 1

```{r}
getwd()
```

## Task 2

### Line A

Line A creates a random sample with replacement of size $n*iter$, from the set $x$. This means that there will be a long vector, with every $n$ elements in the vector representing one, of $iter$, samples. Additionally, sampling with replacement ensures that each random outcome will be independent of all others.

### Line B

Line B calls the quantile function on $xstat$, which is a vector of length $iter$. It contains, by default, the mean value of each $iter$ random samples. By supplying quantile with a sequence of bounds created from $\alpha$, we create a confidence interval that ensures that $\mu$ will have a $(1 - \alpha)*100 \%$ chance of lying in the interval.

### sample()

Sample must be called with replacement, otherwise the random sample collected of size $n$ would not be able to accomodate $n*iter$ unique values being drawn from it.

### commands

```{r}
set.seed(35) 
sam=round(rnorm(20,mean=10,sd=4),2)

#five times
for (i in 0:4)
{
unique(sample(sam,20,replace=TRUE))
}

#five times
for (i in 0:4)
{
unique(sample(sam,20,replace=FALSE))
}
```

In the first function call, sometimes the sample collected will be smaller than the requested sample size because repeats are thrown out. In the second function call, repeat values are accepted, so sometimes they are recorded twice in a single sample.

The line `sample(sam,21,replace=FALSE)` cannot run because the sam is not large enough to collect a sample of 21 elements without replacement.

## Task 3

### myboot(), 95% confidence interval, mean

```{r}
myboot<-function(iter=10000,x,fun="mean",alpha=0.05,...){  

#Notice where the ... is repeated in the code
n=length(x)   #sample size

#Now sample with replacement
y=sample(x,n*iter,replace=TRUE) #A

# Make a matrix with all the resampled values
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) 
# xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2)) #B
# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,main="Histogram of Bootstrap sample statistics",...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=3)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=3)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=3)

return(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}
```

```{r}
#random sample from normal, n=25, mu=25, sigma=10
set.seed(39); sam1 = rnorm(25, 25, 10)
myboot(x=sam1)

#random sample from chisq, n=20, nu=3
set.seed(30); sam2=rchisq(20, df=3)
myboot(x=sam2)

#random sample from gamma, n=30, alpha=2. beta=3
set.seed(40); sam3=rgamma(30, shape=2, scale=3)
myboot(x=sam3)

#random sample from beta, n=20
set.seed(10); sam4=rbeta(20, shape1=3, shape2=4)
myboot(x=sam4)
```
### Normal

For a normal distribution, the point estimate created by a random sample with $n=20$, has $\bar y=23.88$
The true value of $\mu$ is 25.

### Chi-Square

For a Chi-Square, the point estimate created by a random sample with $n = 20$ has $\bar y = 2.94$.
The true value of $\mu = \nu = 3$.

### Gamma

For a Gamma distribution, the point estimate created by a random sample with $n=30$ has $\bar y = 6.5$.
The true vale of $\mu = \alpha \beta = 2*3 = 6$

### Beta

For a Beta distribution, the point estimate created by a random sample with $n=20$ has $\bar y=0.41$.
The true value of $\mu = \frac{\alpha}{\alpha + \beta} = \frac{3}{3+4} = \frac{3}{7} \approx 0.4286$.

### Conclusion

In each case, the true value $\mu$ is within the 95% confidence interval.

### myboot(), 80% confidence interval, variance

```{r}
set.seed(39); sam1 = rnorm(25, 25, 10)
myboot(x=sam1, fun="var")

#random sample from chisq, n=20, nu=3
set.seed(30); sam2=rchisq(20, df=3)
myboot(x=sam2, fun="var")

#random sample from gamma, n=30, alpha=2. beta=3
set.seed(40); sam3=rgamma(30, shape=2, scale=3)
myboot(x=sam3, fun="var")

#random sample from beta, n=20
set.seed(10); sam4=rbeta(20, shape1=3, shape2=4)
myboot(x=sam4, fun="var")
```

## Task 4

### Adjusted myboot()

```{r}
myboot<-function(iter=10000,x,fun="mean",alpha=0.05,...){  

#Notice where the ... is repeated in the code
n=length(x)   #sample size

#Now sample with replacement
y=sample(x,n*iter,replace=TRUE) #A

# Make a matrix with all the resampled values
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) 
# xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2)) #B
# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,main="Histogram of Bootstrap sample statistics",...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=3)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=3)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=3)

return(list(xstat, ci=ci,fun=fun,x=x))# Some output to use if necessary
}
```


### sam=c(1,1,1,2,2,2,2,3,3,3,4,4)

```{r}
sam=c(1,1,1,2,2,2,2,3,3,3,4,4)

bootstrapstat=myboot(x=sam, fun="median")

```

The bootstrap interval estimate is $(1.5, 3)$.

## Task 5

### 95% confidence

```{r}
##function to calculate mean/median, pass to myboot
mean_over_median = function(x)
{
  return (mean(x)/median(x))
}

set.seed(39); sam=rnorm(25,mean=25,sd=10)
bootstat = myboot(x=sam, fun=mean_over_median)

set.seed(30); sam=rchisq(20,df=3)
bootstat = myboot(x=sam, fun=mean_over_median)

set.seed(40); sam=rgamma(30,shape=2,scale=3)
bootstat = myboot(x=sam, fun=mean_over_median)

set.seed(10); sam=rbeta(20,shape1=3,shape2=4)
bootstat = myboot(x=sam, fun=mean_over_median)

```

### 70% confidence

```{r}
set.seed(39); sam=rnorm(25,mean=25,sd=10)
bootstat = myboot(x=sam, fun=mean_over_median, alpha=.3)

set.seed(30); sam=rchisq(20,df=3)
bootstat = myboot(x=sam, fun=mean_over_median, alpha=.3)

set.seed(40); sam=rgamma(30,shape=2,scale=3)
bootstat = myboot(x=sam, fun=mean_over_median, alpha=.3)

set.seed(10); sam=rbeta(20,shape1=3,shape2=4)
bootstat = myboot(x=sam, fun=mean_over_median, alpha=.3)
```

## Task 6

### Uniform Distribution
```{r}
set.seed(1); sam=runif(20, min=0, max = 10)
bootstat=myboot(x=sam, fun="mean", alpha=.2)
bootstat=myboot(x=sam, fun="var", alpha=.2)
```

### F distribution

```{r}
set.seed(2); sam=rf(20, df1=5, df2=3)
bootstat=myboot(x=sam, fun="mean", alpha=.2)
bootstat=myboot(x=sam, fun="var", alpha=.2)
```

### Weibull Distribution

```{r}
set.seed(3); sam=rweibull(20, shape = 2, scale = 4)
bootstat=myboot(x=sam, fun="mean", alpha=.2)
bootstat=myboot(x=sam, fun="var", alpha=.2)
```

### Binomial Distribution

```{r}
set.seed(4); sam=rbinom(20, size = 100, p=.6)
bootstat=myboot(x=sam, fun="mean", alpha=.2)
bootstat=myboot(x=sam, fun="var", alpha=.2)
```

## Task 7

### Bootstrap of Normal for SD and IQR
```{r}
set.seed(68); sam=rnorm(20, mean=10, sd=4)

bootstat=myboot(x=sam, fun="sd")
bootstat=myboot(x=sam, fun="IQR")
```

### Theoretical calculation for mean, 95% confidence interval

```{r}
alpha=0.05
z_alpha_2 = qnorm(1-(alpha/2), mean=0, sd=1)
z_alpha_2

mean(sam)
```

We have found that $z_\frac{\alpha}{2} = 1.959964$ for $\alpha = 0.05$. The mean of our sample was $10.45931$, thus our $95\%$ confidence interval is approximately $(8.499346, 12.419)$.

### Verification

```{r}
bootstate=myboot(x=sam)
```

The $95\%$ confidence interval given from the bootstrap function was $(8.93, 11.89)$, which varies from the true value by $(+0.43, -0.529)$.
